Improving the portuguese hyphenation rules

### 2023-05-02 article/article.tex
new section fix issue #4

In summary, data from \emph{CETENFolha} and \emph{Palavras NET} were compiled.
Their words were hyphenated based on the hyphenation orignal \TeX{} rules and
contrasted with the dictionary results. The performance was appraised and the
errors systematized, in order to find in the literature possible rules that
could complement and improve it.

\section{Grammar rules for hyphenation in Portuguese}

@@

>>>>

In summary, data from \emph{CETENFolha} and \emph{Palavras NET} were compiled.
Their words were hyphenated based on the hyphenation original \TeX{} rules and
contrasted with the dictionary results. The performance was appraised and the
errors systematized, in order to find in the literature possible rules that
could complement and improve it.

\section{Writing systems}\label{sec-writing-systems}

@@

\section{Grammar rules for hyphenation in Portuguese}\label{sec-grammar-port}
